### 2023-07-26 article3.qmd
final corrections for SU and Uliège

UVP6 data and in particular the averaged number of particles per size class (i.e. PSD) was divided by the number of images at each depth and the water volume imaged by the UVP (0.7 L) to obtain particle concentrations (units: #/L). Note that in an impending update by the Coriolis data center, it will no longer be necessary to divide by the number of images.

@@

### Derivation of carbon fluxes from OST

@@

```{r, UVP6 profiling mode without sinking speed small classes, fig.height=8, fig.width=8}
#| label: fig-uvp6-profiling-102-406
#| fig-cap: Vertical profiles of UVP6 particle concentrations for size classes in the 102 - 512 $\mu$m size range. Concentrations were normalized for each size class. The colorbar is in log$_{10}$ scale.

@@

```{r, UVP6 profiling mode without sinking speed large classes, fig.height=8, fig.width=8}
#| label: fig-uvp6-profiling-512-2500
#| fig-cap: Vertical profiles of UVP6 particle concentrations for size classes in the 0.512 - 2.5 mm size range. Concentrations were normalized for each size class. The colorbar is in log$_{10}$ scale. The gray background depicts the absence of particle in the specified size class.

@@

Even though we suggested that the two pairs of floats were deployed in two different bloom regimes, they all measured an increase in particle concentrations in the 102 - 512 $\mu$m range (@fig-uvp6-profiling-102-406) around 800 - 1000 m as well as an increase in the abundance of large particles (@fig-uvp6-profiling-512-2500) between June and August. This increase raises the question of a possible particle export event. For classes \> 512 $\mu$m, the vertical concentration profiles highlight a larger particle plume for the 6904241-1902578 pair than for the other one. However, apart from the float 6904240, all floats measured similar integrated Chla content in the upper 100 m and in the mixed layer (@fig-chla-content). @fig-OST-flux also shows that $F_{small}$ is similar across all floats at all parking depths and that $F_{large}$ is also similar across all floats at 1000 m with an increase from June to August as observed in F$_{small}$. The same behavior is observed for UVP6 particles in the lower size range at 1000 m (@fig-uvp-1000m). Observing similar properties across a wide geographical range around deployments suggests that we observe the latent dynamics of the system rather than episodic export events.

@@

All things considered, it is not straightforward to conclude for the presence of a carbon export event. First, the 10-day profiling configuration hinders the characterization of particle export events that are transient processes. Second, the plume of large particles can be misleading because the abundance measured by the UVP6 are very low (usually \< 0.1 #/L). However, the plume could be the result of aggregation (repackaging) by zooplankton feeding on small particles. Third, all floats measured the same particle dynamics in distinct zones which suggests that if the two systems were initially different (i.e. different bloom dynamics), they merged back after the bloom of May. Therefore, we suggest that we mostly observe the latent dynamics of the system rather than clear export signatures that would likely be spotted with both higher bloom intensities (e.g. the May bloom that was missed) and a higher profiling temporal resolution.

@@

The current configuration of all floats in the LS was a 10-day ascending profile acquisition with drifting at 200 m for one day, 500 m for 3 days and 1000 m for 5 days. During drifting, OST measurements were taken every 30 minutes at all depths whereas UVP measurements were taken every 20 minutes at 200 m and every 2h at 500 m and 1000 m. This initial configuration was based on a compromise between science targets and energy consumption limitations for long-term deployment (years). However, I think this configuration could be adapted depending on the period of the year to target specific processes. For instance, I tried to evaluate sinking speeds from particle concentrations using a gaussian fit in different water layers to follow the gaussian peak with time and depth for each size class. I managed to compute realistic sinking speeds but the uncertainty was huge and potentially biased because I was just trying to fit something I saw in the data. Therefore, I did not use those estimations here but I think it would be possible to compute them if the float was sampling every day when the abundance of particles is at its maximum (e.g. during the spring bloom). Similarly, to address the question of the vertical migration, a 10-day temporal resolution is way to low because plankton images are rare compared to detritus so the sampling volume should be greatly increased to have a better estimation of the presence (or absence) of zooplankton. Finally, it would perhaps be interesting to increase the time spent at 200 m (to 3 days) and decrease the time spent at 1000 m (to 3 days instead of 5) where the probability of capturing big particles is lower than at 200 m. There could also be UVP6 and OST measurements closer in time at all drifting depths to have a better comparison of attenuation slopes/jumps and biovolumes.

>>>>

UVP6 data and in particular the averaged number of particles per size class (i.e. PSD) was divided by the number of images at each depth and the water volume imaged by the UVP (0.7 L) to obtain particle concentrations (units: #/L).

@@

### Derivation of carbon fluxes from the OST

@@

```{r, UVP6 profiling mode without sinking speed small classes, fig.height=8, fig.width=10}
#| label: fig-uvp6-profiling-102-406
#| fig-cap: Vertical profiles of UVP6 particle concentrations for size classes in the 102 - 512 $\mu$m size range. Concentrations were normalized for each size class. The colorbar is in log$_{10}$ scale.

@@

```{r, UVP6 profiling mode without sinking speed large classes, fig.height=8, fig.width=10}
#| label: fig-uvp6-profiling-512-2500
#| fig-cap: Vertical profiles of UVP6 particle concentrations for size classes in the 0.512 - 2.5 mm size range. Concentrations were normalized for each size class. The colorbar is in log$_{10}$ scale. The gray background depicts the absence of particle in the specified size class.

@@

Even though we suggested that the two pairs of floats were deployed in two different bloom regimes, they all measured an increase in particle concentrations in the 102 - 512 $\mu$m range (@fig-uvp6-profiling-102-406) around 800 - 1000 m as well as an increase in the abundance of large particles (@fig-uvp6-profiling-512-2500) between June and August. This increase raises the question of a possible particle export event. For classes \> 512 $\mu$m, the vertical concentration profiles highlight a larger particle plume for the 6904241-1902578 pair than for the other one. However, apart from the float 6904240, all floats measured similar integrated Chla content in the upper 100 m and in the mixed layer (@fig-chla-content). @fig-OST-flux also shows that $F_{small}$ is similar across all floats at all parking depths and that $F_{large}$ is also similar across all floats at 1000 m with an increase from June to August as observed in F$_{small}$. The same behavior is observed for UVP6 particles in the lower size range at 1000 m (@fig-uvp-1000m). Observing similar properties across a wide geographical range around deployments suggests that we observe the latent (i.e. seasonal) dynamics of the system rather than episodic export events.

@@

All things considered, it is not straightforward to conclude for the presence of a carbon export event. First, the 10-day profiling configuration hinders the characterization of particle export events that are transient processes. Second, the plume of large particles can be misleading because the abundance measured by the UVP6 are very low (usually \< 0.1 #/L). However, the plume could be the result of aggregation (repackaging) by zooplankton feeding on small particles. Third, all floats measured the same particle dynamics in distinct zones which suggests that if the two systems were initially different (i.e. different bloom dynamics), they merged back after the bloom of May. Therefore, we suggest that we mostly observe the seasonal dynamics of the system rather than clear export signatures that would likely be spotted with both higher bloom intensities (e.g. the May bloom that was missed) and a higher profiling temporal resolution.

@@

The current configuration of all floats in the LS was a 10-day ascending profile acquisition with drifting at 200 m for one day, 500 m for 3 days and 1000 m for 5 days. During drifting, OST measurements were taken every 30 minutes at all depths whereas UVP measurements were taken every 20 minutes at 200 m and every 2h at 500 m and 1000 m. This initial configuration was based on a compromise between science targets and energy consumption limitations for long-term deployment (years). However, I think this configuration could be adapted depending on the period of the year to target specific processes. For instance, I tried to evaluate sinking speeds from particle concentrations using a gaussian fit in different water layers to follow the gaussian peak with time and depth for each size class. I managed to compute realistic sinking speeds but the uncertainty was huge and potentially biased because I was just trying to fit something I saw in the data. Therefore, I did not use those estimations here but I think it would be possible to compute them if the float was sampling every day when the abundance of particles is at its maximum (e.g. during the spring bloom). Similarly, to address the question of the vertical migration, a 10-day temporal resolution is way too low because plankton images are rare compared to detritus so the sampling volume should be greatly increased to have a better estimation of the presence (or absence) of zooplankton. Finally, it would perhaps be interesting to increase the time spent at 200 m (to 3 days) and decrease the time spent at 1000 m (to 3 days instead of 5) where the probability of capturing big particles is lower than at 200 m. There could also be UVP6 and OST measurements closer in time at all drifting depths to have a better comparison of attenuation slopes/jumps and biovolumes.

### 2023-07-26 discussion.qmd
final corrections for SU and Uliège

This led us to define what we called a trust index, that is a metric whose score indicates the degree of confidence in the classification score. In other words, we looked for the best error estimator (@fig-trust-index). To this end, we trained a first classification model with classes from the UVP5 data set using a `multi:softprob` objective function. Then, we used the model to make a prediction on a test set that returned a matrix $(M \times N)$ of $M$ images and $N$ probabilities ($N$ classes in the model). Afterwards, we computed four metrics on each row of the probability matrix: the maximum probability ($max$, equivalent to `multi:softmax`), the softmax of the probability array ($softmax$, equivalent to a double `multi:softmax`), the difference between the highest and the second highest probability ($diff_{max}$) and the difference between the highest and second highest probability of the softmax array ($diff_{softmax}$). We compared those metrics for each class of the test set in @fig-trust-index which clearly shows that all metrics were very similar and that they captured the errors at the same speed. This result is threefold: 1) in our case, there is no need to use a trust index in addition to the probabilities given by `multi:softprob`, 2) some classes kept accumulating errors in the prediction with increasing rank (e.g. *Copepoda*, darksphere and fiber\<detritus) thus an increasing rank is not always a trustworthy indicator of increasing confidence 3) it partly explains why the quantification did not improve the overall classification by either using a fixed probability threshold (i.e. TC) or using the probability matrix (i.e. SPAC).

@@

This work has shown the first comparison of BGC-Argo floats equipped with both the UVP6 and an OST to better quantify carbon fluxes from particle counts and beam attenuation. If the prediction of carbon fluxes at global scale was not a success, this work has highlighted current difficulties and ways to more forward using machine learning approaches. The deployment of BGC-Argo floats in the frame of REFINE with the combination of UVP6 measurements (particle counts and identification), OST beam attenuation fluxes as well as bio-optical variables (e.g. Chla, $b_{bp}$, incident light) will likely improve our understanding of processes that affect the attenuation of the downward carbon flux at local scale.

>>>>

This led us to define what we called a trust index, that is a metric whose score indicates the degree of confidence in the classification score. In other words, we looked for the best error estimator (@fig-trust-index). To this end, we trained a first classification model with classes from the UVP5 data set using a `multi:softprob` objective function. Then, we used the model to make a prediction on a test set that returned a matrix $(M \times N)$ of $M$ images and $N$ probabilities ($N$ classes in the model). Afterwards, we computed four metrics on each row of the probability matrix: the maximum probability ($max$, equivalent to `multi:softmax`), the softmax of the probability array ($softmax$, equivalent to a double `multi:softmax`), the difference between the highest and the second highest probability ($diff_{max}$) and the difference between the highest and second highest probability of the softmax array ($diff_{softmax}$). We compared those metrics for each class of the test set in @fig-trust-index which clearly shows that all metrics were very similar and that they captured the errors at the same speed. This result is threefold: 1) in our case, there is no need to use a trust index in addition to the probabilities given by `multi:softprob`, 2) some classes kept accumulating errors in the prediction with increasing rank (e.g. *Copepoda*, darksphere and fiber\<detritus) thus an increasing rank is not always a trustworthy indicator of increasing confidence, 3) it partly explains why the quantification did not improve the overall classification by either using a fixed probability threshold (i.e. TC) or using the probability matrix (i.e. SPAC).

@@

This work has shown the first comparison of BGC-Argo floats equipped with both the UVP6 and an OST to better quantify carbon fluxes from particle counts and beam attenuation. If the prediction of carbon fluxes at global scale was not a success, this work has highlighted current difficulties and ways to move forward using machine learning approaches. The deployment of BGC-Argo floats in the frame of REFINE with the combination of UVP6 measurements (particle counts and identification), OST beam attenuation fluxes as well as bio-optical variables (e.g. Chla, $b_{bp}$, incident light) will likely improve our understanding of processes that affect the attenuation of the downward carbon flux at local scale.

### 2023-07-26 index.qmd
final corrections for SU and Uliège

The global carbon cycle had been at close equilibrium for millions of years before the industrial revolution started in the 18th century. Since then, human have been burning fossil fuels at an unprecedented rate, releasing huge amounts of carbon dioxide ($CO_{2}$) in the atmosphere that should have been discharged slowly through the slow carbon cycle [@Bertrand2021-nh]. These emissions, resulting from the burning of fossil fuels but also from land use change (e.g. deforestation, land management) have been estimated around 700 Pg C since 1750 [@Canadell2021-ds].

@@

The solubility pump is responsible for the great majority of all the anthropogenic $CO_{2}$ that has been absorbed by the ocean and it would be contributing to 10% of the observed vertical DIC gradient according to @Sarmiento2006-ec.

@@

| Pump                   | POC export/injection depth range | DOC injection depth range | Sequestration time potential (years) |
|------------------------|----------------------------------|---------------------------|--------------------------------------|
| Gravitational          | export depth - sediment          | None                      | N/A (142)                            |
| Mixed layer            | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Eddy subduction        | 150 - 400 m                      | 150 - 400 m               | up to 150 (N/A)                      |
| Large-scale subduction | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Diel migration         | 200 - 600 m                      | None                      | up to 250 (150$^{c}$)                |
| Seasonal migration     | 600 - 1,400 m$^{a}$              | None                      | up to 500 (N/A)                      |

>>>>

The global carbon cycle had been at close equilibrium for millions of years before the industrial revolution started in the 18th century. Since then, human have been burning fossil fuels at an unprecedented rate, releasing huge amounts of carbon dioxide ($CO_{2}$) in the atmosphere that should have been discharged slowly through the slow carbon cycle [@Bertrand2021-nh]. These emissions, resulting from the burning of fossil fuels but also from land use change (e.g. deforestation, land management), have been estimated around 700 Pg C since 1750 [@Canadell2021-ds].

@@

The solubility pump is responsible for the great majority of all anthropogenic $CO_{2}$ that has been absorbed by the ocean and it would be contributing to 10% of the observed vertical DIC gradient according to @Sarmiento2006-ec.

@@

| Pump                   | POC export/injection depth range | DOC injection depth range | Sequestration time potential (years) |
|-----------------|-------------------|-----------------|---------------------|
| Gravitational          | export depth - sediment          | None                      | N/A (142)                            |
| Mixed layer            | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Eddy subduction        | 150 - 400 m                      | 150 - 400 m               | up to 150 (N/A)                      |
| Large-scale subduction | 200 - 1,000 m                    | 200 - 1,000 m             | 25 - 100 (54$^{b}$)                  |
| Diel migration         | 200 - 600 m                      | None                      | up to 250 (150$^{c}$)                |
| Seasonal migration     | 600 - 1,400 m$^{a}$              | None                      | up to 500 (N/A)                      |

### 2023-07-26 observingCarbonCycle.qmd
final corrections for SU and Uliège

To estimate the downward POC flux, one therefore needs to quantify the amount of POC collected through a given area over a known time period at a given depth. However, the apparent sinking flux measured with sediment traps can be biased due to hydrodynamic issues that could result in over- or under-collection of particles (especially at the surface) or swimmers (zooplankton, small fish) that could enter sediment traps and affect the collected material and solubilization of collected material (e.g. by bacteria) [@Buesseler2007-ql].

@@

```{r, OST on BGC-Argo example with jump}
#| label: fig-estapa-method
#| fig-cap: Application of the method of @Estapa2017-jr on a drifting transmissometer to divide the $c_{p}$ signal into a continuous (dark blue) component, cleaned from spikes and negative jumps (assumed as not related to carbon flux) and a discontinuous (positive jumps, light blue) component. Data from BGC-ARGO float WMO 4903634, drifting at 1000 m during its 9$^{th}$ cycle.
library(tidyverse)
library(ggplot2)
library(vroom)
#library(castr)
library(plyr)
library(scales)
library(lubridate)
library(latex2exp)

@@

The assumption that all particles of a given size class have the same carbon content and settling rate questions the formulation of the model itself (@eq-carbon-flux-finite). It has been shown [@Durkin2021-nq] that the pool of sinking particles is varied (e.g. compact fecal pellets, porous aggregates) and that the main driver of the sinking speed is currently subject to debate [@sec-sinking-speed]. Therefore, the size-dependent model of @Guidi2008-vp could be improved by taking into account the composition and nature of particles [@Durkin2021-nq] and by increasing the number of paired measurements between UVP PSD-derived flux estimates and other direct POC flux estimates (e.g. sediment traps, $^{234}Th$, OST).

@@

1.  BGC-Argo floats equipped with a UVP6 and a zooplankton classification algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited in terms of their battery life. They are typically deployed for several years, which requires to minimize the energy consumption of each sensor. In @sec-uvp6, I will therefore describe the methodology used to develop a zooplankton classification model for the UVP6 accounting for energy limitations.
2.  Four BGC-Argo floats equipped with both an OST and a UVP6 were deployed for the first time in the Labrador Sea in late May 2022 to study the dynamics of carbon fluxes and particle concentrations. In this chapter, I will explore the seasonality of the latter and compare how the two sensors relate as two independent measurements of particle and carbon fluxes.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1,000 m). In @sec-bcp-sequestration, we reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.

>>>>

To estimate the downward POC flux, one therefore needs to quantify the amount of POC collected through a given area over a known time period at a given depth. However, the apparent sinking flux measured with sediment traps can be biased due to hydrodynamic issues that could result in over- or under-collection of particles (especially at the surface) or swimmers (zooplankton, small fish) that could enter sediment traps and affect the collected material or solubilization of collected material (e.g. by bacteria) [@Buesseler2007-ql].

@@

```{r, OST on BGC-Argo example with jump}
#| label: fig-estapa-method
#| fig-cap: Application of the method of @Estapa2017-jr on a drifting transmissometer to divide the $c_{p}$ signal into a continuous (dark blue) component, cleaned from spikes and negative jumps (assumed as not related to the carbon flux) and a discontinuous (positive jumps, light blue) component. Data from BGC-ARGO float WMO 4903634, drifting at 1000 m during its 9$^{th}$ cycle.
library(tidyverse)
library(ggplot2)
library(vroom)
#library(castr)
library(plyr)
library(scales)
library(lubridate)
library(latex2exp)

@@

The assumption that all particles of a given size class have the same carbon content and settling rate questions the formulation of the model itself (@eq-carbon-flux-finite). It has been shown [@Durkin2021-nq] that the pool of sinking particles is varied (e.g. compact fecal pellets, porous aggregates) and that the main driver of the sinking speed is currently subject to debate (@sec-sinking-speed). Therefore, the size-dependent model of @Guidi2008-vp could be improved by taking into account the composition and nature of particles [@Durkin2021-nq] and by increasing the number of paired measurements between UVP PSD-derived flux estimates and other direct POC flux estimates (e.g. sediment traps, $^{234}Th$, OST).

@@

1.  BGC-Argo floats equipped with a UVP6 and a zooplankton classification algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited by their battery life. They are typically deployed for several years, which requires to minimize the energy consumption of each sensor. In @sec-uvp6, I will therefore describe the methodology used to develop a zooplankton classification model for the UVP6 accounting for energy limitations.
2.  Four BGC-Argo floats equipped with both an OST and a UVP6 were deployed for the first time in the Labrador Sea in late May 2022 to study the dynamics of carbon fluxes and particle concentrations. In this chapter, I will explore the seasonality of the latter and compare how the two sensors relate as two independent measurements of particle and carbon fluxes.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1,000 m). In @sec-bcp-sequestration, we reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.
